testibng

### 2024-01-07 Code/R FIle.qmd
better cleaned data; renamed variables

```{r}
# Union Data

union_demographics <- read_rds("../Data/union_demographics.rds")
union_wages <- read_rds("../Data/union_wages.rds")
union_states <- read_rds("../Data/union_states.rds")

@@

```{r}
head(union_demographics)
head(union_wages)
head(union_states)
head(house)
head(income_distribution)
head(minimum_wage)
```

@@

```{r}
summary(demographics)
```

@@

```{r}
union_demographics <- union_demographics |> 
  select(-sample_size) |> 
  mutate(union_type = facet, .keep = "unused")
```

```{r}
union_wages <- union_wages |> 
  select(-sample_size,
         -at_cap) |> 
  mutate(percent_difference = union_wage_premium_raw, .keep = "unused") |> 
  mutate(percent_difference_adjusted = union_wage_premium_adjusted, .keep = "unused") |> 
  mutate(union_type = facet, .keep = "unused")
```

```{r}
union_states <- union_states |> 
  select(-state_census_code,
         -observations)
```

```{r}
income_distribution <- income_distribution |> 
  select(-number) |> 
  select(!ends_with("moe")) |> 
  select(year:income_mean) |> 
  distinct(year, race, income_median, income_mean, .keep_all = TRUE) 
```

```{r}
minimum_wage <- minimum_wage |> 
  select(Year:CPI.Average)
```

>>>>

```{r}
# Union Data
union_wages <- read_rds("../Data/union_wages.rds")
union_states <- read_rds("../Data/union_states.rds")

@@

```{r}
head(union_wages)
head(union_states)
head(house)
head(income_distribution)
head(minimum_wage)
```

@@

@@

```{r}
union_wages <- union_wages |> 
  select(-sample_size,
         -at_cap) |> 
  mutate(wage_percent_difference = union_wage_premium_raw, .keep = "unused") |> 
  mutate(wage_percent_difference_adjusted = union_wage_premium_adjusted, .keep = "unused") |> 
  mutate(union_type = facet, .keep = "unused")
```

```{r}
union_states <- union_states |> 
  select(-state_census_code,
         -observations) |> 
  mutate(employment_count = employment * 1000, .keep = "unused") |> 
  mutate(union_employment_count = members * 1000, .keep = "unused") |> 
  mutate(collective_bargaion_employment_count = covered * 1000, .keep = "unused") |> 
  rename(
    percent_union = p_members,
    percent_collective_bargain = p_covered
  )
```

```{r}
income_distribution <- income_distribution |> 
  select(-number) |> 
  select(!ends_with("moe")) |> 
  select(year:income_mean) |> 
  distinct(year, race, income_median, income_mean, .keep_all = TRUE) |> 
  rename(median_income = income_median,
         mean_income = income_mean)
```

```{r}
minimum_wage <- minimum_wage |> 
  select(Year:CPI.Average) |> 
  rename(year = Year,
         state = State,
         state_min_wage = State.Minimum.Wage,
         state_min_wage_2020_adj = State.Minimum.Wage.2020.Dollars,
         fed_min_wage = Federal.Minimum.Wage,
         fed_min_wage_2020_adj = Federal.Minimum.Wage.2020.Dollars,
         effective_min_wage = Effective.Minimum.Wage,
         effective_min_wage_2020_adj = Effective.Minimum.Wage.2020.Dollars,
         CPI_avg = CPI.Average
  )
```
